---
title: "Working Papers"
author: ""
date: ""
output: 
  html_document: 
    theme: flatly
    highlight: tango
    keep_md: yes
---


<style type="text/css">

h1 {
  font-family: 'Source Sans Pro', sans-serif;
  font-size: 28px;
  color: #333333;
  border-bottom: 2px solid #333333;
  padding-bottom: 10px;
}

h2 {
  font-family: 'Source Sans Pro', sans-serif;
  font-size: 24px;
  color: #444444;
  border-bottom: 1px solid #444444;
  padding-bottom: 8px;
}

h3 {
  font-family: 'Source Sans Pro', sans-serif;
  font-size: 20px;
  color: #555555;
  font-style: italic;
}

body {
  font-family: 'Source Sans Pro', sans-serif;
  font-weight: 400;
}
</style>

```{css, echo = FALSE}

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


 
```{r packages, include=FALSE, message=FALSE, warning=FALSE,results='hide'}
packages <- c("tidyverse","stargazer","AER","asbio","tigerstats","readxl","foreign","wooldridge","moderndive","gridExtra","haven","car") ## This is how you define an object (which is a vector here)
install.packages(packages, repos='http://cran.us.r-project.org') # Installing packages at once
lapply(packages, library, character.only = T) # Loading the packages
```



## [Measuring Income Inequality of Opportunity : Accounting for Dynamic Complementarity (Job Market Paper)](/Slides_4000/Example_Codes.html)

**Abstract**: The egalitarian principle of justice attributes life success to two main factors: circumstances beyond an individual's control and personal effort within it. Roemer's equality of opportunity concept proposes compensating individuals for inequalities arising from unequal circumstances. Dynamic complementarity in skill formation suggests that early childhood skill gaps often persist into adulthood, leading to unequal outcomes. Using PSID data, I classify all measurable factors before the age of majority at 18 as circumstances, creating sets based on critical childhood stages to account for dynamic complementarity. My findings show that over 40% of total income inequality can be attributed to inequality of opportunity before adulthood. Moreover, nearly one-third of total income inequality stems from circumstances faced by individuals at or before age five. Using circumstances identified as important through a random forest—a supervised machine learning model—based on permutation-based importance scores, I estimate the lower bound of inequality of opportunity's share in total inequality before the age of majority to be about 32%. These results underscore the importance of considering childhood circumstances when measuring inequality of opportunity.


## Impact of COVID-19 on Student Performance: Using Exam Level Data from a Public College in NYC, with Theodore Joyce

**Abstract**: We analyze the impact of the COVID-19 pandemic on undergraduates’ performance in an introductory economics course at a large public university. One challenge in analyzing student academic outcomes during the pandemic was the explicit change in grading policies by college administrators as well as the implicit adjustment by faculty designed to mitigate the impact of an abrupt shift to online learning amidst the stress and uncertainly associated with the pandemic. To limit the impact of grading policies we analyze changes in the raw scores on a common final administered to all sections of the course the year before and for four semesters after the spring of 2020. To limit variation in the difficulty of the exams from before to during the pandemic, we compare student performance on nearly identical questions on the final exam overtime. Adjusted mean scores on the common final fell by 0.6 points and the probability of answering the qualitatively same question on the final fell, on average, by 5.7 percentage points. Students with lower GPAs were 4.3 percentage points less likely to answer similar questions correctly relative to students with higher GPAs during the pandemic.


## Measuring the Educational Inequality of Opportunity using Early Childhood Circumstances (work in progress)
